Digital History in Finland, 1488-1828

### 2016-07-01 inst/examples/manuscript-krakow.Rmd
ok

  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell_Johan_Christopher_II.tab)
  * [Frenckell Johan Christopher I](output.tables/Frenckell_Johan_Christopher_I.tab)
  * [Hansson Peter](output.tables/Hansson_Peter.tab)
  * [Londicer Georg Wilhelm](output.tables/Londicer_Georg_Wilhelm.tab)
  * [Wall Johan Larsson](output.tables/Wall_Johan_Larsson.tab)

>>>>

  * [Frenckell Johan Christopher II](output.tables/subjecttopicsFrenckell_Johan_Christopher_II.tab)
  * [Frenckell Johan Christopher I](output.tables/subjecttopicsFrenckell_Johan_Christopher_I.tab)
  * [Hansson Peter](output.tables/subjecttopicsHansson_Peter.tab)
  * [Londicer Georg Wilhelm](output.tables/subjecttopicsLondicer_Georg_Wilhelm.tab)
  * [Wall Johan Larsson](output.tables/subjecttopicsWall_Johan_Larsson.tab)
